Mahotas: Open source software for scriptable computer vision

### 2013-05-06 paper.tex
MIN Read through

Mahotas is released under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} and from the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}). Tutorials and full API
documentation is available online at \url{http://mahotas.readthedocs.org/}.

@@

Numpy arrays contain data of a specific type, such \code{unsigned 8 bit
integer} or floating point numbers. While natural colour images are typically
8~bits, scientific data is often larger (12 and 16~bit formats are common).
Processing can generate floating point images, for example, subtracting the
mean value to every pixel; the mean will be a floating point number even if the
original image was integral. Mahotas works on all datatypes. This is performed
without any extra memory copies. Mahotas is heavily optimised for both speed
and memory usage (it can be used with very large arrays).

@@

Mahotas is mostly written in \cpp, but this is completely hidden from the user
as there are hand-written Python wrappers for all functions. Automatically
generated wrappers inevitably lead to worse error messages and are less
flexible.

The main reason that mahotas is implemented in \cpp{} (and not in C, which is
the language of the Python interpreter) is to use templates. Almost \cpp{}
functionality is split across 2~functions:

@@

Mahotas is implemented in \cpp{}, as the standard Python interpreter is too
slow for a direct Python implementation. However, all of the Python interface
code is hand-written, as opposed to using automatic interface generators like
Swig~\citep{Beazley2003599}. This is more work initially, but the end result is
of much higher quality, especially when it comes to giving useful error
messages. When a type mismatch occurs, an automatic system will often be forced
to resort to a generic message as it does not have any knowledge of what the
arguments mean to the user. It will only know their automatically inferred
types. A hand written system can also automatically convert arguments when
meaningful and be more flexible without completely losing type checking.

>>>>

Mahotas is released under a liberal open source license (MIT License) and is
available from \url{http://github.com/luispedro/mahotas} and from the Python Package
Index (\url{http://pypi.python.org/pypi/mahotas}). Tutorials and full API
documentation are available online at \url{http://mahotas.readthedocs.org/}.

@@

Numpy arrays contain data of a specific type, such \code{unsigned 8 bit
integer} or floating point numbers. While natural colour images are typically
8~bits, scientific data is often larger (12 and 16~bit formats are common).
Processing can generate floating point images. For example, a common
normalization procedure is to subtract from each pixel location the overall
pixel value mean; the result will be a floating point image even if the
original image was integral. Mahotas works on all datatypes. This is performed
without any extra memory copies. Mahotas is heavily optimised for both speed
and memory usage (it can be used with very large arrays).

@@

Mahotas is mostly written in \cpp, but this is completely hidden from the user
as there are hand-written Python wrappers for all functions. The main reason
that mahotas is implemented in \cpp{} (and not in C, which is the language of
the Python interpreter) is to use templates. Almost all \cpp{} functionality is
split across 2~functions:

@@

Mahotas is implemented in \cpp{}, as the standard Python interpreter is too
slow for a direct Python implementation. However, all of the Python interface
code is hand-written, as opposed to using automatic interface generators like
Swig~\citep{Beazley2003599}. This is more work initially, but the end result is
of much higher quality, especially when it comes to giving useful error
messages. When a type mismatch occurs, an automatic system will often be forced
to resort to a generic message as it does not have any knowledge of what the
arguments mean to the user. It will only know their automatically inferred
types. A hand written system can also automatically convert arguments when
meaningful and be more flexible without completely foregoing type checking.
